## Shana Green
## DATA 607 - Homework 3
## Due Date: 9/12/2020

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [The Economic Guide To Picking A College Major](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/), provide code that identifies the majors that contain either "DATA" or "STATISTICS".

```{r}

# Loading data sets for the college majors

majors<-read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")

grep(pattern = 'STATISTICS|DATA', majors$Major, value = TRUE, ignore.case = TRUE)

```

Two results produced STATISTICS and one with DATA. 


### 2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}

fruitveggie<-'[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'


fruitveggie

```


```{r}

#I created an empty vector of fruitveg and I split the elements using the strsplit function by removing the "\" string.

fruitveg<-vector()

splitfruitveggie <- strsplit(fruitveggie,"\"")[[1]]

fruitveg<-splitfruitveggie[c(FALSE,TRUE)]

fruitveg

```

The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

### 3. Describe, in words, what these expressions will match:

```
(.)\1\1
"(.)(.)\\2\\1"
(..)\1
"(.).\\1.\\1"
"(.)(.)(.).*\\3\\2\\1" 
```

**(.)\1\1** matches the same characters that appear three times in a row.
For example, "bbb".

**"(.)(.)\\2\\1"** matches a pair of characters, followed by the same pair in reverse order. For example, "cddc"

**(..)\1** matches any two characters repeated. For example, "f6f6".

**"(.).\\1.\\1"** matches a character, followed by any character, then the original, then any character, and finally the original character. For example, "abada".

**"(.)(.)(.).*\\3\\2\\1"** selects three characters, followed by zero or more characters produced in reversed order. For example, "hij6jih".


# 4. Construct regular expressions to match words that:

Start and end with the same character.

```
str_subset(words, "^(.)((.*\\1$|1?$)") 
```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```
str_subset(words, "([A-Za-z][A-Za-z]).*\\1")
```