---
title: "Assignment – Working with XML and JSON in R"
author: ''
output:
  html_document:
    df_print: paged
  pdf_document:
    extra_dependencies:
    - geometry
    - multicol
    - multirow
---

## Shana Green
## DATA 607 - Homework 7
## Due Date: 10/10/2020

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(jsonlite)
library(rvest)
library(dplyr)
library(RCurl)
library(stringr)
library(arsenal)

```

## Loading books from an HTML file

```{r}
# Loading from HTML
book_a<-as.data.frame(read_html("https://raw.githubusercontent.com/sagreen131/DATA-607-HW-7/main/books.html")%>% html_table(fill=TRUE))

```

```{r}
htmldf <- book_a %>% `colnames<-`(c('Title', 'Authors', 'ISBN', 'Edition', 'Topics'))

htmldf <- select(htmldf, Title, Authors, ISBN, Edition, Topics)
htmldf
```

## Loading books from an XML file


```{r}
library(XML)
```


```{r}
# Loading from XML
book_b <- read_xml("https://raw.githubusercontent.com/sagreen131/DATA-607-HW-7/main/books.xml")

book_b_2 <-xmlParse(book_b)

xmldf <- xmlToDataFrame(book_b_2)
xmldf <- xmldf %>% `colnames<-`(c('Title', 'Authors', 'ISBN', 'Edition', 'Topics'))

```

```{r}
xmldf
```

## Loading books from an JSON file


```{r}
# Loading from JSON
book_c <- fromJSON("https://raw.githubusercontent.com/sagreen131/DATA-607-HW-7/main/books.json")

```

```{r}
jsondf <- as.data.frame(book_c)
jsondf <- jsondf %>% `colnames<-`(c('Title', 'Authors', 'ISBN', 'Edition', 'Topics'))

```

```{r}
jsondf
```


## Summary

The data frames are very similar. The only difference I saw was that the HTML df displayed the ISBN as a double with exponents, as opposed to the character string. I thought it would make sense to assign column names in HTML and XML.


```{r}
summary(comparedf(htmldf,xmldf))
```

Github [here](https://github.com/sagreen131/DATA-607-HW-7.git)




Rpubs [here](https://rpubs.com/sagreen131/673555)
