---
title: "Assignment – Web APIs"
author: "Shana Green"
date: " DATA 607 - Homework 9, Due: 10/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(httr)
library(jsonlite)
```

### Assignment/Introduction

Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. 


I went on the [NY Times API](https://developer.nytimes.com/apis) website and I chose the Books API, since I am a fan of reading books. I chose the “Book Sellers History”. I retrieved info for the history to see the last few best sellers. 


[Link here](https://developer.nytimes.com/docs/books-product/1/overview)

### Preparing Data

```{r}

ex<-GET("https://api.nytimes.com/svc/books/v3/lists/best-sellers/history.json?api-key=AkaADUlHKZkrwFyA3iDtzBbhtuZMECIa")


cat("The status returned is:", ex$status_code)

```
### Converting JSON Data
```{r}
data <- fromJSON(rawToChar(ex$content))
names(data)

```

```{r}
df<-data.frame(data$results, stringsAsFactors = FALSE)

```


### View the data
```{r}
df %>% 
select(title, description, author, publisher, reviews) %>% 
rename("Title" = title, "Description" = description,"Author" = author, "Publisher" = publisher, "Reviews"=reviews) %>% 
kable

```
### Confirm if data frame works

```{r}

tf <- is.data.frame(df)
cat("Is this a dataframe?", tf)
```

### Conclusion 

I was able to retrieve, format and use the API from The New York Times. 